How unprecedented was the February 2021 Texas cold snap?

### 2021-03-23 doc/article.tex
EarthArXiV text

This is a non-peer reviewed preprint submitted to EarthArXiv by James Doss-Gollin, David J. Farnham, Upmanu Lall, and Vijay Modi.
This manuscript has been submitted to \emph{Environmental Research Letters}.
If accepted, a link to the published DOI will be provided here.

>>>>

This is a non-peer reviewed manuscript by James Doss-Gollin, David J. Farnham, Upmanu Lall, and Vijay Modi.
You can find a permanent and updated preprint on EarthArXiV at \url{https://doi.org/10.31223/X5003J}.
This manuscript is still under review; if accepted we will provide a link to the published article here.
